To be FAIR: Theory Specification Needs an Update

### 2025-06-07 manuscript.Rmd
whoops, confused Herbert Simon and Kurt Lewin

We envision a future where application of the FAIR principles makes theories more *useful*, living up to Herbert Simon's ideal,
enabling scholars to incorporate theory into their workflows in a tanglible way,
providing explicit derivation chains for hypotheses,
applying transparent rules to select the right control variables for causal inference,
and proposing specific changes to existing theories based on empirical results.
This paves the way for more theory-driven scholarship
and accelerates cumulative knowledge acquisition in psychology, the social sciences, and beyond.

>>>>

We envision a future where application of the FAIR principles makes theories more *useful*, living up to Kurt Lewin's ideal,
enabling scholars to incorporate theory into their workflows in a tanglible way,
providing explicit derivation chains for hypotheses,
applying transparent rules to select the right control variables for causal inference,
and proposing specific changes to existing theories based on empirical results.
This paves the way for more theory-driven scholarship
and accelerates cumulative knowledge acquisition in psychology, the social sciences, and beyond.
